How Diverse is the MoMA: While Modern, Not Diverse in Its Artists and Directors

### 2023-04-18 outputs/paper/paper.qmd
- Created model drafts

# Set up workspace 
library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
```

@@

# Introduction
Diversity in museums is a topic that is increasingly being discussed and raised as a problem in museums. While the main goal of museums is to serve as cultural institutions and a place of learning, oftentimes the objects on display or the decision-making staff who work behind the scenes do not meet this mission of inclusion.

@@

# Data {#sec-data}
Investigating artists: 
```{r}
#| label: fig-artistnationality
#| fig-cap: Nationality Distribution of Consituents (Artists, Staff) in MoMA Exhibits
#| echo: false

@@

@@

Investigating directors and department heads:
```{r}
#| label: fig-staffnationality
#| fig-cap: Nationality Distribution of Directors and Department Heads in MoMA
#| echo: false

@@

gender_model <-
  lm(
    formula = Gender ~ DepartmentBeginYear,
    data = numeric_momadirectors_data
  )

summary(gender_model)
```

@@

# Discussion
## First discussion point {#sec-first-point}

>>>>

# Set up workspace 
library(tidyverse)
library(dplyr)
library(tidyr)
library(knitr)
library(kableExtra)
library(rstanarm)
library(modelsummary)
```

@@

# Introduction

Diversity in museums is a topic that is increasingly being discussed and raised as a problem in museums. While the main goal of museums is to serve as cultural institutions and a place of learning, oftentimes the objects on display or the decision-making staff who work behind the scenes do not meet this mission of inclusion.

@@

# Data {#sec-data}

Investigating artists:

```{r}
#| label: fig-artistnationality
#| fig-cap: Nationality Distribution of Consituents (Artists, Staff) in MoMA Exhibits
#| echo: false

@@

\newpage

@@

\newpage

Investigating directors and department heads:

```{r}
#| label: fig-staffnationality
#| fig-cap: Nationality Distribution of Directors and Department Heads in MoMA
#| echo: false

@@

potential_gender_model <-
  lm(
    formula = Gender ~ DepartmentBeginYear,
    data = numeric_momadirectors_data
  )

summary(potential_gender_model)
```

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
gender_model <-
  readRDS(file = here::here("outputs/models/gender_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
modelsummary::modelsummary(
  list(
    "First model" = gender_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## Gender distribition {#sec-first-point}

## Nationality distribition {#sec-second-point}

## Analyzing the model: is time a factor? {#sec-third-point}

## Comparing artists vs directors {#sec-fourth-point}

## Weaknesses and next steps

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
#pp_check(first_model) +
#  theme_classic() +
#  theme(legend.position = "bottom")
#posterior_vs_prior(first_model) +
#  theme_minimal() +
#  scale_color_brewer(palette = "Set1") +
#  theme(legend.position = "bottom") +
#  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
#plot(first_model, "trace")
#plot(first_model, "rhat")
```

\newpage
